Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
Update paper.qmd

sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "All 'Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_cybully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'Cyberbullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

sum_schbully_data |> ggplot(aes(x = date, y = sum)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'School Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

@@

@@

@@

\newpage

>>>>

cleaned_bully_data |> ggplot(aes(x = date, 
                                    y = hits,
                                    fill = State.Name)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "All 'Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

cleaned_cybully_data |> ggplot(aes(x = date, 
                                    y = hits,
                                    fill = State.Name)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'Cyberbullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

cleaned_schbully_data |> ggplot(aes(x = date, 
                                    y = hits,
                                    fill = State.Name)) + 
  geom_col() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 8)) +
  labs(
    title = "'School Bullying' Searches in High Asian Population States",
    x = "Date",
    y = "Search Frequency",
    fill = "State Name"
  )

@@

Figure 1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations. According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8). While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline. In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity. On average the 2020 frequency was lower than in previous years. This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person. There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years. This blimp at the start of the pandemic could be a result of students being in lock down with more online time. Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19. This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.

@@

Anti-Asian violence skyrocketed over the pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before. The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles. The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth. (could be apart of introduction)

@@

Google's reported data doesn't consider the sample of users or data points. There is an evident sample bias that takes occurs in this study. The general population can be under or overrepresented. It's unsure which students' searches are being used, making their age and ethnicity unclear. The broad population must be represented and used in our data. User behavior is measured by how many hits particular buzzword use. This measurement can be flawed as students may search other buzzwords or not use the internet to gather research on bullying and how to receive help. Google may only report positive trends and ignore negative ones leaving the data skewed.

People have the fundamental right to privacy in all aspects of life. When on the internet, the average individual is dealing with information about their personal life, health, and sensitive topics they may not want to be shared. When choosing what data to report on, Google must be aware of this and careful that they're not impinging on the fundamental human right of privacy. There needs to be more information out there to educate the public on how their information is being used. The average citizen must be aware that their data is collected and used for reports. Hackers are constantly trying to infiltrate and use users' information for their gain. Security measures need to be introduced to protect search data from unauthorized access. The results an individual gets based on their search relate to their demographic and algorithm. Our dataset needs to be looked at with this in mind. An ethical lens must always be used when looking at people's search data to prevent discriminatory practices.
